Make any stupid plot you want

### 2021-02-16 draft/sections/intro.tex
moving figure, working through checklists

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}

 This work presents a mathematical description of how data is transformed into graphic representations. While many researchers have identified and described important aspects of visualization, they have specialized in such different ways as to not provide a model general enough to natively support the full range of data and visualization types many general purpose modern visualization tools may need to support. In this work, we present a framework for understanding visualization as equivariant maps between topological spaces. Using this mathematical formalism, we can interpret and extend prior work and also develop new tools. We validate our model by using it to re-design artist and data access layer of Matplotlib, a general purpose visualization tool.

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/dar.png}
    \caption{Visualization is equivariant maps between data and visual encoding of the variables and assembly of those encodings into a graphic.
    \note{will replace w/ overarching figure w/ same structure}}
    \label{fig:intro_artist_stages}
\end{figure}

 This work presents a mathematical description of how data is transformed into graphic representations, as shown in ref~\ref{fig:intro_artist_stages}. While many researchers have identified and described important aspects of visualization, they have specialized in such different ways as to not provide a model general enough to natively support the full range of data and visualization types many general purpose modern visualization tools may need to support. In this work, we present a framework for understanding visualization as equivariant maps between topological spaces. Using this mathematical formalism, we can interpret and extend prior work and also develop new tools. We validate our model by using it to re-design artist and data access layer of Matplotlib, a general purpose visualization tool.

### 2021-02-16 draft/sections/math.tex
moving figure, working through checklists

\section{Topological Artist Model}
\label{sec:tam}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/dar.png}
    \caption{Visualization is equivariant maps between data and visual encoding of the variables and assembly of those encodings into a graphic.
    \note{not gonna name these bubbles tau, mu, rho, but might keep the same basic structure of different types of data and encodings }}
    \label{fig:artist_stages}
\end{figure}

@@

We model the data, visual characteristic, and graphic stages of visualization, shown in figure~\ref{fig:artist_stages}, as topological structures that encapsulate types of variables and continuity; by doing so we can develop implementations that keep track of both in ways that let us distribute computation while still allowing assembly and dynamic update of the graphic.

>>>>

\section{Topological Artist Model}
\label{sec:tam}

@@

We model the data, visual characteristic, and graphic stages of visualization as topological structures that encapsulate types of variables and continuity; by doing so we can develop implementations that keep track of both in ways that let us distribute computation while still allowing assembly and dynamic update of the graphic.
